Imperfect slope measurements drive overestimation in geometric cone model of lake and reservoir depth

### 2021-12-07 manuscript/manuscript.Rmd
fig4 caption

\begin{figure}[H]
  \begin{center}
    \includegraphics[width=0.45\textwidth,keepaspectratio]{../figures/00_map_bathy-1.pdf}
  \end{center}
  \caption{Map of study lakes showing A) lake e maximum depth measurements, B) cross-section shape class, and C) reservoir classification. The distribution of lake depths from panel A is reported in Figure S4.}\label{fig2}
\end{figure}

@@

\begin{figure*}
  \begin{center}
    \includegraphics[width=0.75\textwidth,keepaspectratio]{../figures/02_depth_model_grid_resid-1}
  \end{center}
  \caption{Depth model residuals (residual  = observed - predicted) in meters by cross-section shape and reservoir class indicating overprediction of concave and reservoir lakes.}\label{fig4}
\end{figure*}

>>>>

\begin{figure}[H]
  \begin{center}
    \includegraphics[width=0.45\textwidth,keepaspectratio]{../figures/00_map_bathy-1.pdf}
  \end{center}
  \caption{Map of study waterbodies showing A) maximum depth measurements, B) cross-section shape class, and C) reservoir classification. The distribution of lake depths from panel A is reported in Figure S4.}\label{fig2}
\end{figure}

@@

\begin{figure*}
  \begin{center}
    \includegraphics[width=0.75\textwidth,keepaspectratio]{../figures/02_depth_model_grid_resid-1}
  \end{center}
  \caption{Depth model residuals (residual  = observed - predicted) in meters by (a) cross-section shape and (b) reservoir class indicating overprediction of concave and reservoir lakes.}\label{fig4}
\end{figure*}
